Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-07 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Cutting it down to 8 pages

%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_1.png}
    \caption{Deployment B. Weibull Fit.}
    \label{fig:w1}
\end{figure}
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_2.png}
    \caption{Deployment G. Weibull Fit.}
    \label{fig:w2}
\end{figure}

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_3.png}
    \caption{Deployment GG. Weibull Fit.}
    \label{fig:w3}
\end{figure}

@@

% Once again, no model, no relation to the rest of the paper. Either
% you talk about a model of interactions with humans and their
% similarity with the first case study, or you eliminate it. How do
% you tackle boredom? How do you increase engagement? Those are the
% paper's topics, you can't just drop it here because it's interactive
% - JJ
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.2in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.2in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\section{Conclusions}
\label{sec:conclusions}

Volunteer-based and C-IEC systems involve the dynamic 
interaction of many entities and artifacts. Employing a human-centered approach 
can benefit researchers to understand and visualize this kind of systems better.

In this paper a human-centered software framework was proposed, and was validated
through the implementation and refinement of a C-IEC application.
This framework enabled the implementation of a gamification technique 
to improve engagement in a case study which provides a common arena where users are aware of the
activities of other users in the social vicinity.

In concordance with the results obtained in other 
browser-based volunteer systems, after 
applying the gamification techniques, user participation follows the
same pattern and was fitted to a Weibull distribution.

@@

\begin{acks}
  Reserved\\
  Space\\
  for acks\\

>>>>

%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.2in]{img/weibull_1.png}
    \caption{Deployment B. Weibull Fit.}
    \label{fig:w1}
\end{figure}
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.2in]{img/weibull_2.png}
    \caption{Deployment G. Weibull Fit.}
    \label{fig:w2}
\end{figure}

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.2in]{img/weibull_3.png}
    \caption{Deployment GG. Weibull Fit.}
    \label{fig:w3}
\end{figure}

@@

% Once again, no model, no relation to the rest of the paper. Either
% you talk about a model of interactions with humans and their
% similarity with the first case study, or you eliminate it. How do
% you tackle boredom? How do you increase engagement? Those are the
% paper's topics, you can't just drop it here because it's interactive
% - JJ
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.2in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.2in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
  \end{figure}

\section{Conclusions}
\label{sec:conclusions}

Volunteer-based and C-IEC systems involve the dynamic 
interaction of many entities and artifacts. Employing a human-centered approach 
will allow researchers to understand and visualize this kind of
systems better. % But you would have to provide some proof of this - JJ

In this paper a human-centered software framework was proposed, and was validated
through the implementation and refinement of a C-IEC application.
This framework enabled the implementation of a gamification technique 
to improve engagement in a case study which provides a common arena where users are aware of the
activities of other users in the social neighborhood.

After applying the gamification techniques user participation follows the
same pattern and was fitted to a Weibull distribution, which matches
results obtained in other browser-based volunteer systems.
% We would have to check the actual coefficients. - JJ

@@

\begin{acks}
  Reserved\\
  Space for acks.
